---
title: "Stats 141SL Final Project"
author: "Hayley Todd"
output:
  html_document:
    df_print: paged
---

```{r}
setwd("/Users/Hayley/Downloads/Stats Class Material")
finalproj <- read.csv("Statistics Data  - Page 3.csv", na.strings = c("", "NA"))
#View(finalproj)
```

49 people responded to question 2

```{r}
textmine <- finalproj[c(1,3)]
textmine
library(dplyr)

textmine <- textmine %>% na.omit()
textmine$top_words <- as.character(textmine$top_words)

text_df <- tibble(line = 1:length(textmine$top_words), text = textmine$top_words)

library(tidytext)

text_df <- text_df %>% unnest_tokens(word, text)
#words <- as.data.frame(text_df[,2])
#sort(unique(words[,1]))
```

```{r}
q2words <- text_df %>% count(word, sort = T)
q2words
```


Plot of raw words (typos fixed and multiple words combined):

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

#texttrial <- text_df %>%
#  count(word, sort = TRUE)

q2words %>% dplyr::filter(n > 1) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  theme_minimal() +
  coord_flip() 

#text_df <- texttrial
```

Raw words word cloud:

```{r}
library("wordcloud")
set.seed(135719)
wordcloud(words = q2words$word, freq=q2words$n, min.freq = 1, max.words = 150, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(5, "Paired"))
```

Many words had synonyms or similar themes (such as "diversity" and "diverse"), so we decided to combine those to figure out the major word themes.

Cleaning and combining synonyms/similar themes:

```{r}
cleantext <- text_df

applicable <- c(which(cleantext[,2] == "application"), which(cleantext[,2] == "applicantdriven"), which(cleantext[,2] == "realworld"), which(cleantext[,2] == "useful"))
cleantext[applicable, 2] <- "applicable"

##########

difficult <- c(which(cleantext[,2] == "challenging"), which(cleantext[,2] == "hard"), which(cleantext[,2] == "intensive"), which(cleantext[,2] == "advance"), which(cleantext[,2] == "complicated"), which(cleantext[,2] == "overwhelming"), which(cleantext[,2] == "toomuchinformation"), which(cleantext[,2] == "dense"))
cleantext[difficult, 2] <- "difficult"

############

complex <- c(which(cleantext[,2] == "comprehensive"), which(cleantext[,2] == "crossdisciplinary"))
cleantext[complex, 2] <- "complex"

###########

collaborative <- c(which(cleantext[,2] == "collaboration"), which(cleantext[,2] == "cooperation"))
cleantext[collaborative, 2] <- "collaborative"

###########

team <- c(which(cleantext[,2] == "group"), which(cleantext[,2] == "groupwork"), which(cleantext[,2] == "teamwork"), which(cleantext[,2] == "teamworking"), which(cleantext[,2] == "teamoriented"))
cleantext[team, 2] <- "team"

###########

diversity <- c(which(cleantext[,2] == "diverse"))
cleantext[diversity, 2] <- "diversity"

###########

easy <- c(which(cleantext[,2] == "notthathard"), which(cleantext[,2] == "easycourse"), which(cleantext[,2] == "simple"))
cleantext[easy, 2] <- "easy"

############

engaging <- c(which(cleantext[,2] == "engagement"))
cleantext[engaging, 2] <- "engaging"

###########

enjoyable <- c(which(cleantext[,2] == "enjoy"), which(cleantext[,2] == "fun"), which(cleantext[,2] == "joyful"), which(cleantext[,2] == "happy"))
cleantext[enjoyable, 2] <- "enjoyable"

############

positive <- c(which(cleantext[,2] == "good"))
cleantext[positive, 2] <- "positive"

############

interactive <- c(which(cleantext[,2] == "handson"))
cleantext[interactive, 2] <- "interactive"

############

insightful <- c(which(cleantext[,2] == "insight"))
cleantext[insightful, 2] <- "insightful"

############

interesting <- c(which(cleantext[,2] == "intriguing"))
cleantext[interesting, 2] <- "interesting"

###########

manageable <- c(which(cleantext[,2] == "managable"))
cleantext[manageable, 2] <- "manageable"

###########

enlightening <- c(which(cleantext[,2] == "mindopening"), which(cleantext[,2] == "thoughtprovoking"), which(cleantext[,2] == "thinkoutofthebox"), which(cleantext[,2] == "enlighting"), which(cleantext[,2] == "eyeopening"))
cleantext[enlightening, 2] <- "enlightening"

###########

motivational <- c(which(cleantext[,2] == "motivating"))
cleantext[motivational, 2] <- "motivational"

###########

practical <- c(which(cleantext[,2] == "practicality"))
cleantext[practical, 2] <- "practical"

###########

coding <- c(which(cleantext[,2] == "r"), which(cleantext[,2] == "programming"), which(cleantext[,2] == "computers"))
cleantext[coding, 2] <- "coding"

###########

reaction <- c(which(cleantext[,2] == "reactionpaper"))
cleantext[reaction, 2] <- "reaction"

###########

respectful <- c(which(cleantext[,2] == "respect"))
cleantext[respectful, 2] <- "respectful"

###########

special <- c(which(cleantext[,2] == "unique"))
cleantext[special, 2] <- "special"

###########

statistics <- c(which(cleantext[,2] == "stats"), which(cleantext[,2] == "basicstats"), which(cleantext[,2] == "analytical"))
cleantext[statistics, 2] <- "statistics"

###########

concepts <- c(which(cleantext[,2] == "linearregression"), which(cleantext[,2] == "mlr"), which(cleantext[,2] == "slr"), which(cleantext[,2] == "regression"), which(cleantext[,2] == "math"), which(cleantext[,2] == "modeling"))
cleantext[concepts, 2] <- "concepts"

###########
head(cleantext)
q2themewords <- cleantext %>% count(word, sort = TRUE)
q2themewords
```

Plot of cleaned words:

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
#cleantext
#cleantext <- cleantext %>%
#  arrange(desc(n))

q2themewords %>% dplyr::filter(n > 1) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  theme_minimal() +
  coord_flip() 

#cleantext %>%
#  count(word, sort = TRUE) %>%
#  filter(n > 1) %>%
#  mutate(word = reorder(word, n)) %>%
#  ggplot(aes(word, n)) +
#  geom_col() +
#  xlab(NULL) +
#  theme_minimal() +
#  coord_flip()
```

Word Cloud of Cleaned Words:

```{r}
library("wordcloud")
set.seed(2019)
wordcloud(words = q2themewords$word, freq=q2themewords$n, min.freq = 1, max.words = 150, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(5, "Paired"))
```

Some exploratory analysis:

```{r}
page1 <- read.csv("Statistics Data  - Page 1.csv", na.strings = c("", "NA"))
#library(plyr)
#View(page1)

page1$GPA <- ordered(page1$GPA, levels = c("less than 2.5", "2.5 to 3.0", "3.0 to 3.5", "more than 3.5"))

ggplot(page1, aes(x = GPA,fill = Attend)) + geom_bar(position = position_dodge()) + theme_minimal() + coord_flip() + labs(y = "Number of Students")
```

Large amount of students had a GPA of 3.5 or higher. Those who had 3.5 or higher mostly attended 90-100% of classes. People with 3.0-3.5 mostly attended 75% of class. 

```{r}
combo <- cbind(page1, finalproj[,3])
#View(combo)
```

```{r}
cleantext <- cleantext %>% group_by(line) %>% summarise(words = paste(word, collapse=" "))
cleantext$ID <- textmine$ID
cleantext <- cleantext[,-1]
FINALDF <- full_join(combo, cleantext, by = "ID")
FINALDF <- FINALDF[,-21]
FINALDF
```

```{r}
summary(FINALDF)
```

______________________________________________________________________________________________

We wanted to look into the various characteristics and see if different groups expressed different opinions or concerns about the class:

** INTERNATIONAL/NON INTERNATIONAL STUDENTS: **

24 International responses, 25 Non International responses --> even though fewer non-international people in the class, more responded to the question. 

International Student Responses (raw):

```{r}
comboint <- combo[which(combo$INT == "Yes"),]
intwords <- comboint[,21]

combonotint <- combo[which(combo$INT == "No"),]
notintwords <- combonotint[,21]

sum(is.na(comboint[,21]) == F)
sum(is.na(combonotint[,21]) == F)

library(dplyr)

intwords <- intwords %>% na.omit()
intwords <- as.character(intwords)

intwords <- tibble(line = 1:length(intwords), text = intwords)

library(tidytext)

intwords <- intwords %>% unnest_tokens(word, text)
intwordsdf <- as.data.frame(intwords[,2])
#intwordsdf
library(ggplot2)


q2intwords <- intwordsdf %>% 
  count(word, sort = TRUE) %>%
  dplyr::filter(n > 1)

#q2intwords

q2intwords$word <- factor(q2intwords$word, levels = rev(factor(q2intwords$word)))

ggplot(q2intwords, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (International)")
```

International Student Responses (clean):

```{r}
cleanint <- FINALDF[which(FINALDF$INT == "Yes"),]
cleanintwords <- cleanint[,21]

cleannotint <- FINALDF[which(FINALDF$INT == "No"),]
cleannotintwords <- cleannotint[,21]

library(dplyr)

cleanintwords <- cleanintwords %>% na.omit()
cleanintwords <- as.character(cleanintwords)

cleanintwords <- tibble(line = 1:length(cleanintwords), text = cleanintwords)

library(tidytext)

cleanintwords <- cleanintwords %>% unnest_tokens(word, text)
cleanintwordsdf <- as.data.frame(cleanintwords[,2])
#cleanintwordsdf
library(ggplot2)

q2cleanintwords <- cleanintwordsdf %>% 
  count(word, sort = TRUE) %>%
  dplyr::filter(n > 1)
#q2cleanintwords

q2cleanintwords$word <- factor(q2cleanintwords$word, levels = rev(factor(q2cleanintwords$word)))

ggplot(q2cleanintwords, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (International)")
```

Non-International Student Responses (clean):

```{r}
library(dplyr)

cleannotintwords <- cleannotintwords %>% na.omit()
cleannotintwords <- as.character(cleannotintwords)

cleannotintwords <- tibble(line = 1:length(cleannotintwords), text = cleannotintwords)

library(tidytext)

cleannotintwords <- cleannotintwords %>% unnest_tokens(word, text)
cleannotintwordsdf <- as.data.frame(cleannotintwords[,2])

library(ggplot2)

q2cleannotintwords <- cleannotintwordsdf %>% 
  count(word, sort = TRUE) %>%
  dplyr::filter(n > 1)
#q2cleanintwords

q2cleannotintwords$word <- factor(q2cleannotintwords$word, levels = rev(factor(q2cleannotintwords$word)))

ggplot(q2cleannotintwords, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (Non-International)")
```

Top 5 themes for international students: diversity, interesting, enjoyable, team, difficult.

Top 5 themes for non international students: diversity, interesting, applicable, enjoyable, difficult. 

Not very different. 
___________________________________________________________________________________________

**Separating by GPA:**

```{r}
gpa1 <- FINALDF[which(FINALDF$GPA == "less than 2.5"),]
gpa1words <- gpa1[,21]

gpa2 <- FINALDF[which(FINALDF$GPA == "2.5 to 3.0"),]
gpa2words <- gpa2[,21]

gpa3 <- FINALDF[which(FINALDF$GPA == "3.0 to 3.5"),]
gpa3words <- gpa3[,21]

gpa4 <- FINALDF[which(FINALDF$GPA == "more than 3.5"),]
gpa4words <- gpa4[,21]
```

GPA below 2.5:

```{r}
library(dplyr)

gpa1words <- gpa1words %>% na.omit()
gpa1words <- as.character(gpa1words)

gpa1words <- tibble(line = 1:length(gpa1words), text = gpa1words)

library(tidytext)

gpa1words <- gpa1words %>% unnest_tokens(word, text)
gpa1words
gpa1wordsdf <- as.data.frame(gpa1words[,2])
library(ggplot2)

q2gpa1words <- gpa1wordsdf %>% 
  count(word, sort = TRUE) %>%
  dplyr::filter(n > 1)

q2gpa1words$word <- factor(q2gpa1words$word, levels = rev(factor(q2gpa1words$word)))

ggplot(q2gpa1words, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (GPA less than 2.5)")
```

Not many people have GPA below 2.5.

GPA between 2.5 and 3.0:

```{r}
library(dplyr)

gpa2words <- gpa2words %>% na.omit()
gpa2words <- as.character(gpa2words)

gpa2words <- tibble(line = 1:length(gpa2words), text = gpa2words)

library(tidytext)

gpa2words <- gpa2words %>% unnest_tokens(word, text)
gpa2words
gpa2wordsdf <- as.data.frame(gpa2words[,2])
library(ggplot2)

q2gpa2words <- gpa2wordsdf %>% 
  count(word, sort = TRUE) %>%
  dplyr::filter(n > 1)

q2gpa2words$word <- factor(q2gpa2words$word, levels = rev(factor(q2gpa2words$word)))

ggplot(q2gpa2words, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (GPA 2.5 to 3.0)")
```

Also not many people have GPA between 2.5 to 3.0. However, out of those people, most people said "diversity", "difficult", and "interesting". 

GPA between 3.0 and 3.5:

```{r}
library(dplyr)

gpa3words <- gpa3words %>% na.omit()
gpa3words <- as.character(gpa3words)

gpa3words <- tibble(line = 1:length(gpa3words), text = gpa3words)

library(tidytext)

gpa3words <- gpa3words %>% unnest_tokens(word, text)
gpa3words
gpa3wordsdf <- as.data.frame(gpa3words[,2])
library(ggplot2)

q2gpa3words <- gpa3wordsdf %>% 
  count(word, sort = TRUE) %>%
  dplyr::filter(n > 1)

q2gpa3words$word <- factor(q2gpa3words$word, levels = rev(factor(q2gpa3words$word)))

ggplot(q2gpa3words, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (GPA 3.0 to 3.5)")
```

Most use "diversity", "enjoyable", and "interesting".

GPA about 3.5:

```{r}
library(dplyr)

gpa4words <- gpa4words %>% na.omit()
gpa4words <- as.character(gpa4words)

gpa4words <- tibble(line = 1:length(gpa4words), text = gpa4words)

library(tidytext)

gpa4words <- gpa4words %>% unnest_tokens(word, text)
gpa4words
gpa4wordsdf <- as.data.frame(gpa4words[,2])
library(ggplot2)

q2gpa4words <- gpa4wordsdf %>% 
  count(word, sort = TRUE) %>%
  dplyr::filter(n > 1)

q2gpa4words$word <- factor(q2gpa4words$word, levels = rev(factor(q2gpa4words$word)))

ggplot(q2gpa4words, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (GPA 3.5 or more)")
```

Most used "interesting", "diversity", and "applicable". 

Putting all plots together:

```{r}
#summary(FINALDF)
par(mfrow = c(2,2))
ggplot(q2gpa1words, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (GPA less than 2.5)")
ggplot(q2gpa2words, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (GPA 2.5 to 3.0)")
ggplot(q2gpa3words, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (GPA 3.0 to 3.5)")
ggplot(q2gpa4words, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (GPA 3.5 or more)")
```

__________________________________________________________________________________________________________

Recommend:

3/5 did not respond to Page 3 - Question 2. 

```{r}
cleannotrec <- FINALDF[which(FINALDF$Recommend == "No"),]
cleannotrecwords <- cleannotrec[,21]

library(dplyr)

cleannotrecwords <- cleannotrecwords %>% na.omit()
cleannotrecwords <- as.character(cleannotrecwords)

cleannotrecwords <- tibble(line = 1:length(cleannotrecwords), text = cleannotrecwords)

library(tidytext)

cleannotrecwords <- cleannotrecwords %>% unnest_tokens(word, text)
cleannotrecwordsdf <- as.data.frame(cleannotrecwords[,2])
#cleanintwordsdf
library(ggplot2)

q2cleannotrecwords <- cleannotrecwordsdf %>% 
  count(word, sort = TRUE) #%>%
#  filter(n > 1)

q2cleannotrecwords$word <- factor(q2cleannotrecwords$word, levels = rev(factor(q2cleannotrecwords$word)))

ggplot(q2cleannotrecwords, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (No Recommend)")
```

Not many people did not recommend the class. 

------------------------------------------------------------------------------------------------------

**Statistics Majors vs Non-Statistics Majors:**

```{r}
finalpage1 <- read.csv("Copy of Statistics Data  - Page 1.csv", na.strings = c("", "NA"))
finalpage3 <- read.csv("Copy of Statistics Data  - Page 3.csv", na.strings = c("", "NA"))
finalpage1$words <- finalpage3[,3]

library(dplyr)
#textmine <- textmine %>% na.omit()

finalpage1$words <- as.character(finalpage1$words)

majortext_df <- tibble(line = 1:length(finalpage1$words), text = finalpage1$words)

library(tidytext)

majortext_df <- majortext_df %>% unnest_tokens(word, text) %>% na.omit()
majortext_df

cleanmajortext <- majortext_df

applicable <- c(which(cleanmajortext[,2] == "application"), which(cleanmajortext[,2] == "applicantdriven"), which(cleanmajortext[,2] == "realworld"), which(cleanmajortext[,2] == "useful"))
cleanmajortext[applicable, 2] <- "applicable"

##########

difficult <- c(which(cleanmajortext[,2] == "challenging"), which(cleanmajortext[,2] == "hard"), which(cleanmajortext[,2] == "intensive"), which(cleanmajortext[,2] == "advance"), which(cleanmajortext[,2] == "complicated"), which(cleanmajortext[,2] == "overwhelming"), which(cleanmajortext[,2] == "toomuchinformation"), which(cleanmajortext[,2] == "dense"))
cleanmajortext[difficult, 2] <- "difficult"

############

complex <- c(which(cleanmajortext[,2] == "comprehensive"), which(cleanmajortext[,2] == "crossdisciplinary"))
cleanmajortext[complex, 2] <- "complex"

###########

collaborative <- c(which(cleanmajortext[,2] == "collaboration"), which(cleanmajortext[,2] == "cooperation"))
cleanmajortext[collaborative, 2] <- "collaborative"

###########

team <- c(which(cleanmajortext[,2] == "group"), which(cleanmajortext[,2] == "groupwork"), which(cleanmajortext[,2] == "teamwork"), which(cleanmajortext[,2] == "teamworking"), which(cleanmajortext[,2] == "teamoriented"))
cleanmajortext[team, 2] <- "team"

###########

diversity <- c(which(cleanmajortext[,2] == "diverse"))
cleanmajortext[diversity, 2] <- "diversity"

###########

easy <- c(which(cleanmajortext[,2] == "notthathard"), which(cleanmajortext[,2] == "easycourse"), which(cleanmajortext[,2] == "simple"))
cleanmajortext[easy, 2] <- "easy"

############

engaging <- c(which(cleanmajortext[,2] == "engagement"))
cleanmajortext[engaging, 2] <- "engaging"

###########

enjoyable <- c(which(cleanmajortext[,2] == "enjoy"), which(cleanmajortext[,2] == "fun"), which(cleanmajortext[,2] == "joyful"), which(cleanmajortext[,2] == "happy"))
cleanmajortext[enjoyable, 2] <- "enjoyable"

############

positive <- c(which(cleanmajortext[,2] == "good"))
cleanmajortext[positive, 2] <- "positive"

############

interactive <- c(which(cleantext[,2] == "handson"))
cleantext[interactive, 2] <- "interactive"

############

insightful <- c(which(cleanmajortext[,2] == "insight"))
cleanmajortext[insightful, 2] <- "insightful"

############

interesting <- c(which(cleanmajortext[,2] == "intriguing"))
cleanmajortext[interesting, 2] <- "interesting"

###########

manageable <- c(which(cleanmajortext[,2] == "managable"))
cleanmajortext[manageable, 2] <- "manageable"

###########

enlightening <- c(which(cleanmajortext[,2] == "mindopening"), which(cleanmajortext[,2] == "thoughtprovoking"), which(cleanmajortext[,2] == "thinkoutofthebox"), which(cleanmajortext[,2] == "enlighting"), which(cleanmajortext[,2] == "eyeopening"))
cleanmajortext[enlightening, 2] <- "enlightening"

###########

motivational <- c(which(cleanmajortext[,2] == "motivating"))
cleanmajortext[motivational, 2] <- "motivational"

###########

practical <- c(which(cleanmajortext[,2] == "practicality"))
cleanmajortext[practical, 2] <- "practical"

###########

coding <- c(which(cleanmajortext[,2] == "r"), which(cleanmajortext[,2] == "programming"), which(cleanmajortext[,2] == "computers"))
cleanmajortext[coding, 2] <- "coding"

###########

reaction <- c(which(cleanmajortext[,2] == "reactionpaper"))
cleanmajortext[reaction, 2] <- "reaction"

###########

respectful <- c(which(cleanmajortext[,2] == "respect"))
cleanmajortext[respectful, 2] <- "respectful"

###########

special <- c(which(cleanmajortext[,2] == "unique"))
cleanmajortext[special, 2] <- "special"

###########

statistics <- c(which(cleanmajortext[,2] == "stats"), which(cleanmajortext[,2] == "basicstats"), which(cleanmajortext[,2] == "analytical"))
cleanmajortext[statistics, 2] <- "statistics"

###########

concepts <- c(which(cleanmajortext[,2] == "linearregression"), which(cleanmajortext[,2] == "mlr"), which(cleanmajortext[,2] == "slr"), which(cleanmajortext[,2] == "regression"), which(cleanmajortext[,2] == "math"), which(cleanmajortext[,2] == "modeling"))
cleanmajortext[concepts, 2] <- "concepts"

###########

cleanmajortext <- cleanmajortext %>% group_by(line) %>% summarise(words = paste(word, collapse=" "))
finalpage1$line <- c(1:70)
cleanmajortext <- dplyr::full_join(finalpage1, cleanmajortext, by = "line")
cleanmajortext <- cleanmajortext[,-c(21:22)]
```


```{r}
statsmajor <- cleanmajortext[which(cleanmajortext$Major == "Statistics"),]
statsmajorwords <- statsmajor[,21]

nonstatsmajor <- cleanmajortext[which(cleanmajortext$Major != "Statistics"),]
nonstatsmajorwords <- nonstatsmajor[,21]
```

Words Used by Statistics Majors (clean):

```{r}
library(dplyr)

statsmajorwords <- statsmajorwords %>% na.omit()
statsmajorwords <- as.character(statsmajorwords)

statsmajorwords <- tibble(line = 1:length(statsmajorwords), text = statsmajorwords)

library(tidytext)

statsmajorwords <- statsmajorwords %>% unnest_tokens(word, text)
statsmajorwords
statswordsdf <- as.data.frame(statsmajorwords[,2])
library(ggplot2)

q2statswords <- statswordsdf %>% 
  count(word, sort = TRUE) %>%
  dplyr::filter(n > 1)

q2statswords$word <- factor(q2statswords$word, levels = rev(factor(q2statswords$word)))

ggplot(q2statswords, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (Stats Majors)")
```

Words Used by Non-Statistics Majors:

```{r}
library(dplyr)

nonstatsmajorwords <- nonstatsmajorwords %>% na.omit()
nonstatsmajorwords <- as.character(nonstatsmajorwords)

nonstatsmajorwords <- tibble(line = 1:length(nonstatsmajorwords), text = nonstatsmajorwords)

library(tidytext)

nonstatsmajorwords <- nonstatsmajorwords %>% unnest_tokens(word, text)
nonstatsmajorwords
nonstatswordsdf <- as.data.frame(nonstatsmajorwords[,2])
library(ggplot2)

q2nonstatswords <- nonstatswordsdf %>% 
  count(word, sort = TRUE) %>%
  dplyr::filter(n > 1)

q2nonstatswords$word <- factor(q2nonstatswords$word, levels = rev(factor(q2nonstatswords$word)))

ggplot(q2nonstatswords, aes(x = word, y = n, fill = word)) + geom_bar(stat = "identity") + coord_flip() + theme_minimal() + theme(legend.position = "none") + labs(y ="Number of Students (Non Stats Majors)")
```

Graphically Depicting Words Used by Statistics Majors vs Non-Statistics Majors:

- 50/50 split between Statistics and Non-Statistics Majors (including double majors). 

```{r}
majorcombo <- dplyr::full_join(q2nonstatswords, q2statswords, by = "word")
colnames(majorcombo)[c(2,3)] <- c("nonstats","stats")
majorcombo <- majorcombo %>% replace_na(list(nonstats = 0, stats = 0))


library(ggrepel)
ggplot(majorcombo, aes(x = stats, y = nonstats, col = word, label = word)) + geom_point() + theme_minimal() + theme(legend.position = "none") + geom_abline(intercept = 0, slope = 1) + geom_text_repel(aes(label = word), size = 2.5)
```

